Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?

### 2017-07-21 paper.tex
Update on Overleaf.

@@

\comment[FLN]{opportunity for social science to emancipate from the very strong hypotheses of physicists that have become standards (homogeneity and isotropy of space), even though they are never valid in social systems.} \comment[MLT]{Du coup, ça je le garderais plutôt pour la discussion, à moins que l'on avance des références explicites mais je crois que la sous-section d'après explicite assez bien ce besoin.}

>>>>

\comment{Ajouter un paragraphe sur le lien entre forme de grille et comportement du modèle/résultats.}

@@

\comment[FLN]{opportunity for social science to emancipate from the very strong hypotheses of physicists that have become standards (homogeneity and isotropy of space), even though they are never valid in social systems.}
